### 2019-11-07 report/paper.tex
Add first draft of prolonged conclusion.

\documentclass[11pt]{article}
\usepackage[OT4]{fontenc}
\newtheorem{define}{Definition}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\oddsidemargin=0.15in
\evensidemargin=0.15in
\topmargin=-.5in
\textheight=9in
\textwidth=6.25in

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/waldo_winter} 
    \caption{Image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green.}
    \label{fig:waldo-winter}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after k-means preprocessing (originally gray-scaled, but color mapped for display purposes).}
    \label{fig:preprocessed-samples}
\end{figure}

@@

\begin{figure}[]
    \centering
    \begin{subfigure}{0.6\linewidth}
    \begin{tabular}{lcccc}
        \toprule
        class & precision & recall & \( F_1 \) score & \#samples \\
        \midrule
           waldo &  1.00 &  0.69 & 0.82 &  13 \\
           wenda &  0.80 &  0.57 & 0.67 &   7 \\
          wizard &  0.00 &  0.00 & 0.00 &   3 \\
        negative &  0.69 &  1.00 & 0.82 &  20 \\
        \bottomrule
    \end{tabular}
    \end{subfigure}
    \begin{subfigure}{0.35\linewidth}
    \includegraphics[width =\linewidth]{figures/confusion_matrix}
    \end{subfigure}

    \caption{Classification accuracies for waldo, wenda, wizard and negative classes on the HOG/HOV and SVM classifier
    with confusion matrix between the classes to the right.}
    \label{tab:classification_acc}
\end{figure}

\begin{table}[]
    \centering
    \begin{tabular}{lccccc}
        \toprule
        method & \( I_1 \) IoU & \( I_2 \) IoU & \( I_3 \) IoU & Mean IoU & Mean Time \\
        \midrule
        Histogram correlation   & 0.8   & 0.8 & 0.8 & 1s \\
        HOG \& SVM              &0.8    & 1.0 & 0.8 & 1s \\
        HOG/HOV \& SVM          & 0.8   & 1.0 & 0.8 & 1s \\
        \bottomrule
    \end{tabular}
    \caption{Comparison over three cropped image regions, containing one image class each with IoU (Intersection over Union) given for each image.
    Also the mean computation time is given.}
    \label{tab:dataset-stats}
\end{table}

\begin{equation*}
    \text{precision} = \frac{|TP|}{|TP| + |FP|}  
    \quad
    \text{recall} = \frac{|TP|}{|TP| + |FN|}
    \quad
    F_1 = 2\cdot \frac{\text{precision} \cdot \text{precall}}{\text{precision} + \text{recall}}
\end{equation*}

\begin{figure}[]
    \centering
    \begin{subfigure}{0.3\linewidth}
    \includegraphics[width =\linewidth]{figures/detections_1}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \includegraphics[width =\linewidth]{figures/detections_3}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \includegraphics[width =\linewidth]{figures/detections_2}
    \end{subfigure}

    \caption{Classification accuracies for waldo, wenda, wizard and negative classes on the HOG/HOV and SVM classifier
    with confusion matrix between the classes to the right.}
    \label{fig:detections}
\end{figure}

@@

\section{Conclusion}
In this project, we managed to make use of several computer vision techniques and algorithms that we had learnt in class, and put them into practice. Although the results are not perfect, with the presence of several false positives, we managed to be able to detect some instances of the characters using our proposed solution. Which, given the timeline and schedule, is quite an achievement in its own.

\section{Group Information}
\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

>>>>

\documentclass[11pt]{article}
\usepackage[OT4]{fontenc}
\newtheorem{define}{Definition}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{booktabs}
\oddsidemargin=0.15in
\evensidemargin=0.15in
\topmargin=-.5in
\textheight=9in
\textwidth=6.25in

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.845\linewidth]{figures/waldo_winter} 
    \caption{Image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green.}
    \label{fig:waldo-winter}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after k-means preprocessing (originally gray-scaled, but color mapped for display purposes).}
    \label{fig:preprocessed-samples}
\end{figure}

@@

@@

Looking at the results our classifier produced for the test images, it appears that the internal
representation of our classes is not distinctive enough to achieve a very good classification performance.
An example for a classification error that undergirds this hypothesis can be seen in TBD

\section{Conclusion}
In this project, we useed several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.

\section{Group Information}

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    % \hline
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
